Democracy, Public Support, and Measurement Uncertainty

### 2021-06-26 paper/dcpo_demsupport_appendix.Rmd

```{r expanded_claassen}
# these are estimates based on Claassen's original dataset, plus all additional country-year-item observations we found; see

@@

```{r apsr_1k}
ec_df_theta_apsr <- purrr::map(1:1000, function(x) {
  exp_claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_ec_country, .cols = starts_with("V")) %>% 
    mutate(year = ec_first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(sd_controls_apsr, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

>>>>

```{r expanded_claassen_ajps}
# these are estimates based on Claassen's original dataset, plus all additional country-year-item observations we found; see

@@

```{r expanded_claassen_apsr}
ec_df_theta_apsr <- purrr::map(1:1000, function(x) {
  exp_claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_ec_country, .cols = starts_with("V")) %>% 
    mutate(year = ec_first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(sd_controls_apsr, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})
